Hypertension and microbiome

### 2019-08-28 articletwo.Rmd
Deseq code and logistic model sample size calculation

    if("clean" %in% names(args)) {
        unlink("rds", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
    if ("tags" %in% names(args)) 
        rtags('~/phd/research/articletwo/', recursive = FALSE, pattern = '\\.[RrSs](rw|md)?$',
              ofile = '~/phd/research/articletwo/TAGS', verbose = TRUE, append = FALSE)
    if ("loadlast" %in% names(args) )
        load(paste0("session/", sort(list.files("session"), decreasing = TRUE)[1]))
    if ("subset" %in% names(args))
        subset.run <- as.numeric(args$subset)
}

#packrat::opts$ignored.packages
```

@@

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(nortest)
library(microbiome)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(parallel)
library(officer)
library(flextable)
library(xtable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
library(pander)
library(ggpubr)
library(broom)
library(ggfortify)
library(RColorBrewer)
library(gvlma)
library(purrr)
library(pwr)
library(gtable)
library(car)
library(M3C)
library(emmeans)
```

@@

```{r t-sne, eval = FALSE}
sne.df <- pseq.genus %>%
    microbiome::transform(transform = "clr") %>%
    psmelt %>%
    spread(OTU, Abundance)

sne_names <- colnames(sne.df) %>% mygrep(word = "g_")

sne.t <- sne.df %>% select(Sample, HYPERTENSION, sne_names[1:20]) %>%
    mutate(HYPERTENSION = as.numeric(HYPERTENSION)) %>%
    gather(variable, value, -Sample) %>% 
    spread(Sample, value) %>%
    column_to_rownames("variable")

png("sample.png", 800, 800)
tsne(sne.t[-1,], labels = as.factor(sne.t[1,]),
     dotsize = 1)
dev.off()

### CONTINUOUS

source("tsne.R")

sne.t <- sne.df %>% select(Sample, oMAP, sne_names) %>%
    gather(variable, value, -Sample) %>% 
    spread(Sample, value) %>%
    column_to_rownames("variable")

tsne.g <- tsne(sne.t[rownames(sne.t) != "oMAP",],
               labels = as.numeric(sne.t[rownames(sne.t) == "oMAP",]),
               dotsize = 1,
               controlscale = TRUE,
               scale = 2,
               low = "white")

tsne.plot <- tsne.g +
    scale_fill_gradientn(limits = c(-3,3),
                         colours=c("navyblue", "darkmagenta", "darkorange1"),
                         breaks=c(0,200), labels=format(c(0,200)))

ggsave(file = "cache/tsne.png", plot=tsne.plot, height=6, width=9)

@@

@@

>>>>

    if("clean" %in% names(args)) {
        unlink("rds", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
    if ("tags" %in% names(args)) 
        rtags('~/phd/research/articletwo/', recursive = FALSE, pattern = '\\.[RrSs](rw|md)?$',
              ofile = '~/phd/research/articletwo/TAGS', verbose = TRUE, append = FALSE)
    if ("loadlast" %in% names(args) )
        load(paste0("session/", sort(list.files("session"), decreasing = TRUE)[1]))
    if ("subset" %in% names(args))
        subset.run <- as.numeric(args$subset)
}
```

@@

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(nortest)
library(microbiome)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(parallel)
library(officer)
library(flextable)
library(xtable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
library(pander)
library(ggpubr)
library(broom)
library(ggfortify)
library(RColorBrewer)
library(gvlma)
library(purrr)
library(pwr)
library(gtable)
library(car)
library(M3C)
library(emmeans)
library(DESeq2)
```

@@

@@

```{r deseq2, eval = FALSE}
pseq.genus.core.deseq <- pseq.genus %>% core(detection = 0.0001, prevalence = 0.01)

dds.data <- phyloseq_to_deseq2(pseq.genus.core.deseq,
                               as.formula(sprintf("~ %s + %s", "MAP", paste0(var.CL, collapse = "+"))))

dds = DESeq(dds.data, test="Wald", fitType="parametric")
resultsNames(dds)
res = results(dds)
```

@@

Required sub sample size

```{r required sodium subsample size}
lapply(c2l(seq(1, 1.7, 0.05)), function(or) 
    powerMediation::powerLogisticCon(n = nrow(df.genus.salt),
                                     p1 = 0.4,
                                     OR = or)) %>%
    map_df(., ~as.data.frame(.x), .id = "or") %>%
    kable
```
